\documentclass[letterpaper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
% Use Times New Roman font
\usepackage{newtxtext,newtxmath}

% Page style and spacing
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlist{nosep,leftmargin=*}

% Section formatting: 12pt headings
\titleformat{\section}{\fontsize{13pt}{15pt}\selectfont\scshape}{}{0em}{}[\color{black}\titlerule]
\titlespacing*{\section}{0pt}{2pt}{2pt}

% Ensure machine-readable PDF
\pdfgentounicode=1

% List commands
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt,label={},itemsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=\textbullet,leftmargin=0.2in,itemsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}
% Subheading: Title left, date right, then description left with GPA/date bolded right
\newcommand{\resumeSubheading}[4]{\item {\textbf{#1}}\hfill{\textbf{#2}}\\
  {#3}\hfill{\textbf{#4}}}
\newcommand{\resumeItem}[1]{\item #1}

% Document start
\begin{document}
\vspace*{-0.35in}

%----------HEADING----------
\begin{center}
  {\fontsize{15pt}{16pt}\selectfont\bfseries Joseph Spagnoli}\\
  \vspace{2pt}
  {\normalsize 561-329-2705 \textbar\ \href{mailto:jspagnoli1705@gmail.com}{jspagnoli1705@gmail.com} \textbar\ 
  \href{https://www.linkedin.com/in/joseph-spagnoli/}{linkedin.com/in/joseph-spagnoli} \textbar\ 
  \href{https://github.com/joeyspagnoli}{github.com/joeyspagnoli}}
\end{center}

%-----------EDUCATION-----------
\section{\textbf{Education}}
\resumeSubHeadingListStart
  \resumeSubheading{University of Florida $|$ Gainesville}{Aug. 2023 -- May 2027}{Bachelor of Science in Computer Science, Minors: Statistics, Electrical Engineering}{GPA: 4.0}
  \item Certificates in AI Fundamentals and Applications and Data Analytics
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{\textbf{Experience}}
\resumeSubHeadingListStart
  \item {\textbf{Software Engineering Co-op}} \hfill {\textbf{Jan. 2026 -- Present}}\\
    \textbf{GE Appliances $|$ Louisville, KY}
  \resumeItemListStart
    \resumeItem{Incoming co-op on the \textbf{iOS Mobile Applications} team, contributing to feature development in \textbf{Swift} using the \textbf{VIPER} architecture.}
  \resumeItemListEnd

  \item {\textbf{AI Scholars Researcher}} \hfill {\textbf{Aug. 2025 -- Present}}\\
    \textbf{M.E. Rinker, Sr. School of Construction Management $|$ University of Florida}
  \resumeItemListStart
    \resumeItem{Researching an early-warning ML task to \textbf{reduce occupational noise risk} by predicting whether a construction worker will exceed \textbf{NIOSH recommended} daily noise exposure limits by shift's end, using only the first half of a worker’s shift.}
    \resumeItem{Engineering \textbf{time-series} and \textbf{frequency-based features} and comparing \textbf{candidate models} using appropriate evaluation metrics to determine the best approach for practical safety alerts.}
  \resumeItemListEnd
  \item {\textbf{System Administrator Intern}} \hfill {\textbf{May 2025 -- Present}}\\
    \textbf{IFAS $|$ University of Florida}
  \resumeItemListStart
    \resumeItem{Managed technology needs for \textbf{25+ faculty}, providing technical support and leading system maintenance, imaging, and deployment to ensure seamless technology integration and reliability.}
    \resumeItem{Created a dedicated laptop OU in Active Directory and linked a custom GPO to automate biweekly maintenance, running Dell Command Update and Windows security updates every other Sunday.}
  \resumeItemListEnd
   \item {\textbf{AI Engineer Intern}} \hfill {\textbf{Jun. 2025 -- Aug. 2025}}\\
    \textbf{Amentum $|$ NASA Johnson Space Center (JSC)}
  \resumeItemListStart
    \resumeItem{Reduced manual anomaly detection time by \textbf{12 hours} by assisting in the development of an \textbf{autoencoder} using \textbf{PyTorch} to detect anomalies for ISS ARED machine sensor faults, processing over \textbf{11,000 data points} per exercise set in \textbf{large-scale time-series data}.}
    \resumeItem{Engineering a comprehensive dashboard using \textbf{Dash, Plotly, and SciPy}, implemented a \textbf{CI/CD pipeline} with \textbf{PyTest} and GitLab runners to ensure code quality and deployed an \textbf{end-to-end data pipeline} with \textbf{Dagster}.}
  \resumeItemListEnd
  \item {\textbf{Undergraduate Research Assistant}} \hfill {\textbf{Oct. 2024 -- May 2025}}\\
    \textbf{M.E. Rinker, Sr. School of Construction Management $|$ University of Florida}
  \resumeItemListStart
    \resumeItem{Developed a \textbf{CTGAN synthesizer} using \textbf{SDV} and Python to generate high-fidelity synthetic data, enabling initial \textbf{neural network training} in the absence of real-world data.}
    \resumeItem{Identified and analyzed key \textbf{physiological (5–8)} and \textbf{environmental (12–13)} variables to inform early model development for predicting heat-related illness risk in construction settings.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\textbf{Projects}}
\resumeSubHeadingListStart
  \item{\textbf{ExperienceCurator AI $|$ Python, FastAPI, PostgreSQL, pgvector, LangChain, Docker, React/TypeScript}}\hfill\textbf{Dec. 2025 -- Present}
  \resumeItemListStart
  \resumeItem{Built a local-first \textbf{“career memory”} system to \textbf{ingest docs} + \textbf{codebases}, normalize content, \textbf{generate embeddings}, and serve evidence-grounded answers through a \textbf{FastAPI REST API} with \textbf{pgvector retrieval}.}
  \resumeItem{Implemented an \textbf{agent-orchestrated RAG workflow} with evidence-backed \textbf{resume tailor} + \textbf{interview question bank}, cutting resume tailoring time \textbf{30\%} via more representative, \textbf{citation-grounded} bullet suggestions and generating concise, sourced answers to user-created interview questions.}
  \resumeItemListEnd

  \item{\textbf{EvoChess $|$ Python, PyTorch, MLflow, Dagster, AWS S3, Docker, Google Cloud Run}}\hfill\textbf{Mar. 2025 -- Apr. 2025}
  \resumeItemListStart
  \resumeItem{Orchestrated an \textbf{automated MLOps pipeline} with \textbf{Dagster} to \textbf{ETL} chess game data from Lichess into an \textbf{AWS S3 bucket} for CNN model training with \textbf{PyTorch}, and deployed the final model as a containerized API using \textbf{Docker} and \textbf{Google Cloud Run}.}
  \resumeItem{Trained a \textbf{Convolutional Neural Network} in \textbf{PyTorch} on a filtered dataset of over \textbf{9,000,000 2000+ elo rated games}, engineering a data processing workflow to predict optimal move sequences from any given board state.}
  \resumeItemListEnd

  \item{\textbf{Data-Driven Resource Optimization $|$ Python, Matplotlib, Scikit-learn}}\hfill\textbf{Jul. 2024 -- Aug. 2024}
  \resumeItemListStart
    \resumeItem{Developed a \textbf{gradient descent} algorithm to \textbf{minimize} the \textbf{Mean Squared Error (MSE)} for predicting event resource needs}
    \resumeItem{Visualized cost function progression using \textbf{Matplotlib} and validated model performance, achieved a \textbf{R² score} of \textbf{0.958} with \textbf{Scikit-learn}, reduced costs by 20\% and an \textbf{85\%} decrease in waste.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS AND ACHIEVEMENTS-----------
\section{\textbf{Skills and Achievements}}
\resumeSubHeadingListStart
  \item{\textbf{Languages}: Python, C++, R, Java, SQL, JavaScript, TypeScript \textbf{Databases}: PostgreSQL (pgvector), MongoDB, InfluxDB, MySQL}
  \item{\textbf{Cloud \& DevOps}: AWS (S3), Google Cloud Platform (Cloud Run), Linux, Dagster, Docker, Grafana, CI/CD, Git}
  \item{\textbf{Libraries/Frameworks}: Scikit-learn, PyTorch, Pandas, LangChain, SQLAlchemy, Alembic, SDV, React, Dash, Plotly}
  \item{\textbf{Awards}: Amentum Intern Scholarship (2025), AI Scholar (2025), UF President's Honor Roll (2024--Present), Machen Florida Opportunity Scholar (2023)}
  
\resumeSubHeadingListEnd

\end{document}
